### 2016-02-07 prepReport/theorBack.tex
Started LSTM Theoretical Chapter

FALAR EM BPTT

Even though RNNs outperform static ANNs in sequence recognition problems~\cite{Bengio1991}, they fail to retain long-term dependencies. Of course that the weight training process is itself a form of memory, but the problem is that the weight update is much slower than the activations~\cite{Yoshua01}, and therefore this memory only retains short-term dependencies. This is because of the so-called \textbf{Vanishing Gradients Problem}~\cite{Yoshua94,Yoshua01}, where the error decays exponentially through time, and the impact of previous incoming data points on the training of the weights quickly decrease.

To overcome this issue, Hochreiter and Schmidhüber proposed, in 1997, a novel approach, called the Long-Short Term Network~\cite{Hoch97}. The next section explains the main structure of this approach, and also how it is trained, serving as a support basis for the work of this thesis.

@@

>>>>

The training of an RNN is usually performed using a variation of Backpropagation, called \textbf{Backpropagation Through Time} (BPTT), that as the name implies, performs the same backpropagation procedure discussed for the ANNs, but now taking into account the unfolding of the network through a fixed training epoch $T$ like Figure~\ref{fig:recneuron}. Due to this very fact, this training procedure is memory and performance consuming, and so it will not be used in my final work, but instead a novel approach, the \textbf{Simulatneous Perturbation Stochastic Approximation}.

Even though RNNs outperform static ANNs in sequence recognition problems~\cite{Bengio1991}, they fail to retain long-term dependencies. Of course that the weight training process is itself a form of memory, but the problem is that the weight update is much slower than the activations~\cite{Yoshua01}, and therefore this memory only retains short-term dependencies. This is because of the so-called \textbf{Vanishing Gradients Problem}~\cite{Yoshua94,Yoshua01}, where the error decays exponentially through time, and the impact of previous incoming data points on the training of the weights, and thus the current decision, quickly decreases.

To overcome this issue, Hochreiter and Schmidhüber proposed, in 1997, a novel approach, called the Long-Short Term Network~\cite{Hoch97}. The next section explains the main idea of this approach~\ref{sec:struct_lstm}, and also how it is trained\ref{sec:training_lstm}, serving as a support basis for the work of this thesis.

@@

\subsection{Structure, Operation and Equations}\label{sec:struct_lstm}

\subsection{Training -- SPSA}\label{sec:training_lstm}
